Recreation of figures and results in the manuscript

### 2024-03-25 inst/hankin-ejs.Rmd
minor rewording
typo: change printed value of evaluate

@@

It returns this:

@@

```{r plotolymp}
plotolymp <- function(...){
plot(a,L,type='l',ylab="log-likelihood",lwd=2)
abline(h=c(0,-2))
ahat <- optolym$maximum
segments(x0=ahat,y0=-1.5,y1=0)
text(ahat,-0.91,expression(hat(a)==0.573),pos=2)
abline(v=0.5,lty=3)

>>>>

Following is a `sage`-compatible input:

@@

`sage` returns this:

@@

```{r plotolymp}
plotolymp <- function(...){
plot(a,L,type='l',ylab="log-likelihood",lwd=2)
abline(h=c(0,-2))
ahat <- optolym$maximum
segments(x0=ahat,y0=-1.5,y1=0)
text(ahat,-0.91,expression(hat(a)==0.474),pos=2)
abline(v=0.5,lty=3)
